Responses to Reviews

### 2016-07-11 RMS/responses.tex
responsed more comments

@@

>>>>

Thank you for the approval.

Yes, we also agree that Theorem 2 is important. We would consider
including the detailed proof in the printed version, if the page limit
of TIE permits.

@@

Thanks for the pros and the careful reading.

``monus'' is the name of the built-in minus operation defined in
Real-Time Maude, as we introduced in Lemma A.1 at page 8 in the
Appendix. It is not a typo. We have also spell checked the whole
manuscript again to avoid typos.
